---
title: "Midterm"
author: "Han Liu"
date: "7/18/2023"
output: html_document
---
Roadmap:
1.Time series: the data is the monthly retail sales of electricity in the United States from U.S Energy Information Administration

2.Data split: use the first four year of data to build three models + one ensemble model(average of the three forecast for the last year) 


##Load Data 
```{r}
setwd('/Users/hanliu/Downloads')
mydata =read.table ("/Users/hanliu/Downloads/Retail_sales_of_electricity_United_States_monthly.csv", sep = ",", header = TRUE)

```

##Clean Data
```{r}

library(tidyverse)
library(tsibble)

# data column
colnames(mydata)[1] ="Month"
colnames(mydata)[2] ="Commercial_million_kilowatthours"
mydata = mydata[-1,]

mydata = mydata %>%
  mutate (Month = yearmonth(Month))%>%
  tsibble(index = Month)

mydata$Commercial_million_kilowatthours <- as.numeric(mydata$Commercial_million_kilowatthours)

```

##My time series 
```{r}
library(ggplot2)
library(ggfortify)
library(feasts)
myts = ts(mydata$Commercial_million_kilowatthours, start = c(2001,1), frequency = 12)

autoplot(myts) +
  labs(x = "Month", y = "Electricity Consumed (Million Kilowatthours)", title = "Time Series for US Retail Sales of Electricity in Commercial Sector (Monthly)")

mydata %>% gg_season(Commercial_million_kilowatthours, labels = "both") + ylab ("Electricity Consumed")

```

## Time series Evaluation
```{r}

library(forecast)
#the number of non-seasonal differences needed to make a time series stationary
ndiffs(myts)
#the number of seasonal differences needed to make a time series stationary
nsdiffs(myts)

myts %>% 
  diff(lag=12) %>% 
  ggtsdisplay()

```


##Training and Test Set
```{r}

mydata$Month <- as.Date(mydata$Month)

# Split the data into training and test sets based on the specified date ranges
mydata.train <- mydata[mydata$Month <= as.Date("2017-12-31"), ]
mydata.test <- mydata[mydata$Month >= as.Date("2018-01-01"), ]

myts.train <- window(myts, end=c(2017,12))
myts.test <- window(myts, start=2018)

autoplot(myts) +
  autolayer(myts.train, series="Training") +
  autolayer(myts.test, series="Test")
```


## 2.1 Build auto Arima Model
```{r}
library(forecast)
fit_arima = auto.arima(myts.train)
checkresiduals(fit_arima)

#Ljung-Box Test
for (i in 1:30){
  print(Box.test(fit_arima$residuals,lag=i,type='Ljung-Box'))
}

myarima_predict1 = forecast(fit_arima,24)

plot(myarima_predict1)



```
```{r}
# Calculating the accuracy of ARIMA forecasts

acc.arima=accuracy(myarima_predict1,myts.test)
cat("Accuracy of ETS Forecasts\n ")
acc.arima
```



#2.2 Build ETS Model
```{r}
datats = window(myts.train, start=2001)
fit_ets <- ets(datats)
summary(fit_ets)
autoplot(fit_ets)

myets_predict2=forecast(fit_ets, 24)

checkresiduals(fit_ets)
plot(myets_predict2)
```


```{r}

# Calculating the accuracy of ETS forecasts
acc.ets=accuracy(myets_predict2, myts.test)
cat("Accuracy of ETS Forecasts\n ")
print(acc.ets)
```


##2.3 Build snaive model 
```{r}
fit_snaive <- snaive(myts.train)
checkresiduals(fit_snaive)

mysnaive_predict3=forecast(fit_snaive, h=24)
plot(mysnaive_predict3)
```


```{r}
# Calculating the accuracy of snaive forecasts
acc.snaive=accuracy(mysnaive_predict3, myts.test)
cat("Accuracy of snaive Forecasts\n ")
print(acc.snaive)
```

## 2.4 Build ensemble model for the last year
```{r}
forecast_ets <- myets_predict2$mean
forecast_arima <- myarima_predict1$mean
forecast_snaive <- mysnaive_predict3$mean
fit.ensemble <- (forecast_ets + forecast_arima + forecast_snaive) / 3
autoplot(fit.ensemble)
myensemble_predict4=forecast(fit.ensemble, 24)

checkresiduals(myensemble_predict4)

plot(myensemble_predict4, main = "Forecasts from Ensemble Model")


```


```{r}
# Calculating the accuracy of forecasts
acc.ensemble=accuracy(myensemble_predict4, myts.test)
cat("Accuracy of ETS Forecasts\n ")
print(acc.ensemble)

```


